---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = TRUE
)
library(actinet)
library(reticulate)
options(digits.secs = 3)
```

# actinet

<!-- badges: start -->
[![R-CMD-check](https://github.com/jhuwit/actinet/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jhuwit/actinet/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jhuwit/actinet/graph/badge.svg)](https://app.codecov.io/gh/jhuwit/actinet)
<!-- badges: end -->

The goal of `actinet` is to wrap up the https://github.com/OxWearables/actinet algorithm.

# Installation

## Install `actinet` Python Module

See https://github.com/OxWearables/actinet?tab=readme-ov-file#install for how to install the `actinet` python module.  In the new `reticulate`, you can do this via:

```{r}
Sys.setenv(
  RETICULATE_PYTHON = "managed"
)
reticulate::py_require("actinet==0.7.2", python_version = "3.10")
sc <- reticulate::import("actinet")
```
This will install actinet via `uv` **every time** you run the command a new time.


You can also install a conda environment via: 

```{r, eval = FALSE}
envname = "actinet"
reticulate::conda_create(envname = envname, packages = c("python=3.10"))
Sys.unsetenv("RETICULATE_PYTHON")
reticulate::use_condaenv(envname)
reticulate::py_install("actinet", envname = envname, method = "conda", pip = TRUE)
```

Once this is finished, you should be able to check this via:

```{r, eval = FALSE}
actinet::have_actinet()
```

The `actinet_check` function can determine if the `actinet` module can be loaded and run:

```{r actinet_check}
actinet::actinet_check()
```

In some cases, you ay want to set `RETICULATE_PYTHON` variable:

```{r, eval = FALSE}
clist = reticulate::conda_list()
Sys.setenv(RETICULATE_PYTHON = clist$python[clist$name == "actinet"])
reticulate::use_condaenv("actinet")
```


# Usage

## Running `actinet` (file)
The main function is `actinet::actinet`, which takes can take in a file directly:

```{r run_actinet_file}
library(actinet)
library(dplyr)
library(ggplot2)
library(tidyr)
file = system.file("extdata/P30_wrist100.csv.gz", package = "actinet")
if (actinet_check()) {
  out = actinet(file = file)
}
```

Let's see inside the output, which is a list of values, namely a `data.frame` of `steps` with the time (in 10s increments) and the number of steps in those 10 seconds, a `data.frame` named `walking` which has indicators for if there is walking within that 10 second period:

```{r actinet_output}
names(out)
str(out)
```


